---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# pprof

This is Google's [pprof](https://github.com/google/pprof) tool for visualization and analysis of profiling data, wrapped as an R package. It exports a single function which returns the path to the executable file.

The `pprof` binary can also be installed via `go get github.com/google/pprof`. However, some operating systems have an incompatible version of `pprof` on the `PATH` by default. This R package offers an easy-to-use robust alternative.

## Installation

You can install *pprof* from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("r-prof/r-pprof")
```

## Example

```{r example, message=TRUE}
invisible(processx::run(
  pprof::get_pprof_path(),
  "-help",
  echo = TRUE,
  error_on_status = FALSE
))
```
